Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-02-11 ms/cover_letter/plosHIVcover_resubm2.tex
almost last edits to ms ...

The point about initial virulence being measured immediately after
a species jump is interesting, but since it is somewhat peripheral
to our main exploration here, we have opted to include in the 
Discussion rather than trying to squeeze it into the abstract
\todo{don't forget to do this}
}

@@

\response{make sure we have a caveat/comment in text}

@@

\response{same thing again}

>>>>

The point about initial virulence being measured immediately after
a species jump is interesting, but seems peripheral
to our goals for this paper.
}

@@

\response{We now discuss this issue (l. 500).}

@@

\response{This is essentially the same point as above; we have tried to 
temper our conclusions on lines 60 and 500.}
